Visualizing Functional Data

### 2017-05-09 sections/sectionnd.tex
new outline
somehow lost my sections...

\begin{document}
\section{Independent Observations (0D fields)}

\subsection{Univariate Observations}
%%histogram and pdfs/distribution fitting

\subsection{Bivariate Observations}
%%introduce box plot

\subsection{Multivariate Observations}
%% large scale box: letter, spark

\subsection{Relationships Between Variables}
\subsubsection{Bivariate}
%%scatter segue into bagplot and HDR?

\subsection{Multivariate Observations}

%% radial, parallel coordinates, factor plotl
%%high d-PCA, ICA, markov

>>>>

\begin{document}
\section{ND Fields}
Toolkits, all the Toolkits.

overview-zoom/filter-details-on-demand is the guiding mantra for many of the
tools built to visiaulzie demnsionally complex data \cite{shneiderman1996eyes}
because these tools facilitate engagment with the data at the aggregate and
encourage drilling down to the core. Some of the most widley used of these
tools are:
*parview
*vistrails
*...

\subsection{Independent Variables}
\subsection{Univariate Observations}
Toolkits, all the Toolkits.

%cite my calender paper here!
subspace decomposition, projection persuite, manifolds,
spation temporal viz, yield curve
\subsection{Bivariate Observations}

\subsection{Relationships Between Variables}
\subsubsection{Bivariate}
\subsection{Multivariate Observations}
